Competing Bandits: The Perils of Exploration under Competition

### 2018-09-04 paper/content/sim_details.tex
This file is now obsolete!

@@

@@

We fix the sliding window size $M = 100$. We found that low values of $M$ induced too much random noise in the results, and increasing $M$ further did not make a substantial qualitative difference. Unless otherwise noted, all results are reported at $t = 2000$. \gaedit{The simulations are computationally intensive with each experiment usually taking around half a day parallelized over a cluster of 12 CPU cores.}

>>>>

OBSOLETE!

@@

\subsubsection{Terminology.}
\asedit{Following a standard game-theoretic terminology, algorithm Alg1 \emph{(weakly) dominates} algorithm Alg2 for a given firm if Alg1 provides a larger (or equal) market share than Alg2 at the end of the game. An algorithm is a (weakly) dominant strategy for the firm if it (weakly) dominates all other algorithms. This is for a particular MAB instance and a particular selection of the game parameters.}

\OMIT{\gaedit{Since the algorithms that involve exploration have larger deployment costs, we break any indifference towards algorithms that do not involve exploration (i.e. if \DG and \DEG provide the same market share, the firm will play \DG).}}

@@

We fix the sliding window size $M = 100$. We found that lower values induced too much random noise in the results, and increasing $M$ further did not make a qualitative difference. Unless otherwise noted, \asedit{we used $T = 2000$}.

\asedit{The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 XX Hz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about XX hours.}
